Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-08-03 source/jeb_tex/manuscript.tex
Linear mixed model results included in supplementary info.
Reviewer 1 and 3 responded and changes made in MS.
Reviewer 2 typo suggestions included

\corres{(\email{endlein01@mpip-mainz.mpg.de}; \email{xxxx@xxxx.xxx.xx})}

@@

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \citep{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\citep{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \citep{RN221} and \emph{Epilachna vingtipunctuata} \citep{RN222}, rendering it immiscible with water.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focused our study only on a single tarsal adhesive pad of the leg by carefully immobilizing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth untreated and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

\subsection{Material and Methods}

@@

The adult seven-spotted male ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with natural daylight. They were fed with raisins, honey and
water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were used within three weeks of being housed under above conditions.

 %The beetle's leg was constrained similar to the method described by Bullock et al \citep{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder (roughly 3 mm water level). The beetle was then partially 
submerged to allow underwater contact of the pad with the substrate. In order to achieve contact without
a trapped air bubble, the water was first degassed separately in a vacuum chamber
at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. Before the experiments,
the pad was brought into contact with the clean dry surface 10 times repeatedly 
to ensure the hairs are free of any contaminating particles.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

Data sets were compared for statistical differences using two-way ANOVA analysis, with \emph{contact mode} and \emph{substrate chemistry} as the categorical variables and \emph{adhesion force} as the dependant variable. Pairwise
Student t-test were done for post-hoc analysis and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the ANOVA 
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow before use. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in an oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic untreated glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

The surface chemistry was characterised by dynamic contact angle
measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany})
The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu l s\protect\textsuperscript{-1} flow rate (see supplementary section S2).

@@

In air, adhesion forces of the distal pad of ladybug beetle against
glass and PFOTS were similar, i.e. no significant differences were
detected (Figure \ref{fig:Effect-of-contact} and supplementary section S3).
In contrast, the underwater adhesion on a PFOTS surface was significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
was observed both in the presence and absence of a trapped bubble.
In both cases, the adhesion force reached similar values as in air. In contrast,
on glass, adhesion underwater was significantly reduced when compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). In the presence of a bubble, underwater adhesion on glass was slightly higher (CLES = 0.84, p = 0.07).

@@

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary data: Movie2), unlike the other
three contact modes (supplementary data: Movie1). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume, $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

@@

The capillary force, $f$, is the sum of two contributions: surface
tension and Laplace pressure. Force
versus distance for a single capillary bridge was calculated by Surface
Evolver simulations\citep{RN206}  (see supplementary section S1 for details),
and used to obtain $F_{net}$ as a function of $d$ for each mode
of contact. The adhesion force of the complete hairy pad system was
then obtained from the minima of $F_{net}$, where negative force
values represent attraction.

@@

Here, $\theta_{fw}$ and $\theta_{fa}$ are the contact angles of
the tarsal adhesive fluid with the substrate in water and air respectively,
$\theta_{wa}$ is the contact angle of water with the substrate in
air, $\gamma_{fa}$ is the surface tension of the tarsal adhesive fluid,
$\gamma_{wa}$ is the surface tension of water and $\gamma_{fw}$
is the interfacial tension of the tarsal adhesive fluid with water.

All lengths ($D_{h}$, $D_{p}$, $L$, $d$) were normalised w.r.t. $s_{f}$ and forces were normalized
w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values were fixed relative
to $\gamma_{fa}$. Non dimensional bubble volume was expressed as,
$\hat{V}_{b}=V_{b}/s_{f}^{3}$

Geometric parameters and interfacial properties were kept fixed for
all model calculations (Table \ref{tab:Model-parameters}). Here,
we assumed the tarsal adhesive fluid to be an oil-like substance and thus the
interfacial tension ratios $\gamma_{wa}/\gamma_{fa}$ and $\gamma_{fw}/\gamma_{fa}$
were assumed to correspond to typical values for oil and water. We considered
representative hydrophilic and hydrophobic substrates with $\theta_{fa}$
and $\theta_{wa}$ values corresponding to a typical glass and fluorinated
surface, respectively. The contact area fraction of the hairs relative to the
pad, $\alpha=ND_{h}^{2}/D_{p}^{2}$, hair aspect ratio, $L/D_{h}$,
and fluid size parameter, $\phi_{f}$, were fixed to values typical
for a ladybug's hairy pad.

@@

\begin{table}[!t]
\processtable{Fixed parameters corresponding to the pad's geometry, 
tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
\hline
\TCH{Property} & \TCH{Value} \\
\hline
Contact area fraction, $\alpha$ & 0.1\\
Hair aspect ratio, $L/D_{h}$ & 10\\
Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\\
Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\\
Tarsal fluid size parameter, $\phi_{f}$ & 2\\
\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=24\lyxmathsym{\textdegree}$\\
\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=50\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=120\lyxmathsym{\textdegree}$
\end{tabular*}}{}
\end{table}

@@

The force-distance curves show a general trend of repulsive forces
at small distances (Figure \ref{fig:Single-bridge}a). This is a result
of the pinned contact line on the top. A limited volume is available
for the liquid to occupy when the gap distance is small, causing the
meniscus shape to bulge outwards near the pinned contact line. This
creates a net positive curvature, resulting in a positive Laplace
pressure and thus repulsion. Without pinning, the capillary forces
would have shown high attractive forces on a hydrophilic substrate\citep{RN93}.

\subsection{Adhesion of a hairy pad: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}

@@

We observed that the bubble itself doesn't contribute much to the net force
on either substrate (Figure \ref{fig:Effect-of-substrate}). Its contribution
even is slightly repulsive on the hydrophilic substrate due to the
positive curvature of the bubble, and slightly attractive on the hydrophobic
substrate due to its negative curvature. This small contribution is
manifested by the slightly higher adhesion for \emph{underwater: bubble}
relative to \emph{in air} for the hydrophobic substrate, since all
hairs are within the bubble in this case.

>>>>

\corres{(\email{endlein01@mpip-mainz.mpg.de})}

@@

\section{Summary statement}

Fluid-mediated adhesion seen in animals such as ladybug beetles allows them to attach to surfaces not just in air but also in underwater conditions.

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored. Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids requires the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \citep{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\citep{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \citep{RN221} and \emph{Epilachna vingtipunctuata} \citep{RN222}, rendering it immiscible with water.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focused our study only on a single tarsal adhesive pad of the leg by carefully immobilizing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth untreated and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion forces
for each of the labelled contact modes were compared for both substrates.

\subsection{Materials and Methods}

@@

Adult seven-spotted male ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with natural daylight. They were fed with raisins, honey and
water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were used within three weeks of being housed under above conditions.

 %The beetle's leg was constrained similar to the method described by Bullock et al \citep{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. The front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack from its claws and tibia using a pair of tweezers without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights (range: 2 - 90 mg) to get the corresponding force (resolution = 5 \textmu N). A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to measure the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion were done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder (roughly 3 mm water level). The beetle was then partially 
submerged to allow underwater contact of the pad with the substrate (immersion time $\sim$ 15 mins). In order to achieve contact without
a trapped air bubble, the water was first degassed separately in a vacuum chamber
at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. The beetle was subsequently immersed, where, the trapped air bubble within the pad dissolves into the degassed water in less than 5 mins, as verified by the ventral view contact image. Before the experiments,
the pad was brought into contact with the clean dry surface 10 times repeatedly 
to ensure the hairs are free of any contaminating particles.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force curve with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

Data sets were compared for statistical differences using two-way ANOVA analysis, with \emph{contact mode} and \emph{substrate chemistry} as the categorical variables and \emph{adhesion force} as the dependant variable. Pairwise
Student t-test were done for post-hoc analysis and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk tests were done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the ANOVA 
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow before use. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in an oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150 \textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic untreated glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

The surface chemistry was characterised by dynamic contact angle
measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany}).
The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu l s\protect\textsuperscript{-1} flow rate (see supplementary section S2).

@@

In air, adhesion forces of the distal pad of the ladybug beetles against
glass and PFOTS were similar, i.e. no significant differences were
detected (Figure \ref{fig:Effect-of-contact} and supplementary section S3).
In contrast, the underwater adhesion on a PFOTS surface was significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
was observed both in the presence and absence of a trapped bubble.
In both cases, the adhesion force reached similar values as in air. In contrast,
on glass, adhesion underwater was significantly reduced when compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). In the presence of a bubble, underwater adhesion on glass was slightly higher (CLES = 0.84, p = 0.07).

@@

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary data: Movie2), unlike the other
three contact modes (supplementary data: Movie1). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air bubble trapped within
them which might not have completely dissolved away in the water.
The presence of this air-water meniscus could thus lead to elasto-capillary bundling of the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

@@

The capillary force, $f$, is the sum of two contributions: Laplace pressure and  surface
tension, as given by:
\begin{equation}
f=\varDelta P_{laplace}A_{_{bottom}}+2\pi R_{bottom}\gamma\sin\theta\label{eq:f_bridge}
\end{equation}

Here, $\varDelta P_{laplace}$ is the Laplace pressure of the equilibrium
capillary bridge, $\theta$ is the contact angle, $A_{bottom}$ is the contact area of the capillary
bridge with the substrate at bottom and $R_{bottom}$ is the corresponding
radius of contact. Unlike previous analytical treatments \citep{RN203, RN318}, force versus distance for a single capillary bridge was calculated by Surface
Evolver simulations \citep{RN206, RN93},
and used to obtain $F_{net}$ as a function of $d$ for each mode
of contact  (see supplementary section S1 for details). The adhesion force of the complete hairy pad system was
then obtained from the minima of $F_{net}$, where negative force
values represent attraction.

@@

Here, $\theta_{fw}$ and $\theta_{fa}$ are the contact angles of
the tarsal adhesive fluid with the substrate in water and air respectively,
$\theta_{wa}$ is the contact angle of water with the substrate in
air, $\gamma_{fa}$ is the surface tension of the tarsal adhesive fluid,
$\gamma_{wa}$ is the surface tension of water and $\gamma_{fw}$
is the interfacial tension of the tarsal adhesive fluid with water.
%
%All lengths ($D_{h}$, $D_{p}$, $L$, $d$) were normalised w.r.t. $s_{f}$ and forces were normalized
%w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values were fixed relative
%to $\gamma_{fa}$. Non dimensional bubble volume was expressed as,
%$\hat{V}_{b}=V_{b}/s_{f}^{3}$

Geometric parameters and interfacial properties were kept fixed for
all model calculations (Table \ref{tab:Model-parameters}). Here,
we assumed the tarsal adhesive fluid to have similar interfacial tension values as n-hexadecane \citep{RN320}. Experimental receding contact angle values for n-hexadecane and water
on untreated (hydrophilic) and fluorinated (hydrophobic) glass surface were used as 
 $\theta_{fa}$ and $\theta_{wa}$, respectively (Table S1).
Hair and pad geometry, and tarsal fluid volume were assumed to be values typical
for a ladybug's hairy pad \citep{RN19, RN108}.

@@

%\begin{table}[!t]
%\processtable{Fixed parameters corresponding to the pad's geometry, 
%tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
%{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
%\hline
%\TCH{Property} & \TCH{Value} \\
%\hline
%Contact area fraction, $\alpha$ & 0.1\\
%Hair aspect ratio, $L/D_{h}$ & 10\\
%Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\\
%Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\\
%Tarsal fluid size parameter, $\phi_{f}$ & 2\\
%\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
%    & $\theta_{wa}=24\lyxmathsym{\textdegree}$\\
%\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=50\lyxmathsym{\textdegree}$\\
%    & $\theta_{wa}=120\lyxmathsym{\textdegree}$
%\end{tabular*}}{}
%\end{table}

\begin{table}[!t]
\processtable{Fixed parameters corresponding to the pad's geometry, 
tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
\hline
\TCH{Property} & \TCH{Value} \\
\hline
Number of hairs, $N$ & 500\\
Hair diameter, $D_{h}$ & 4 \textmu m\\
Pad diameter, $D_{p}$ & 200 \textmu m\\
Hair length, $L_{h}$ & 40 \textmu m\\
Water surface tension, $\gamma_{wa}$ & 72 mN m\textsuperscript{-1}\\
Tarsal fluid-air surface tension, $\gamma_{fw}$ & 27 mN m\textsuperscript{-1}\\
Tarsal fluid-water interfacial tension, $\gamma_{fw}$ & 55 mN m\textsuperscript{-1}\\
Tarsal fluid volume, $V_{f}$ & 4 fL\\
Bubble volume, $V_{b}$ & 1 nL\\
\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=20\lyxmathsym{\textdegree}$\\
\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=56\lyxmathsym{\textdegree}$\\
    & $\theta_{wa}=93\lyxmathsym{\textdegree}$
\end{tabular*}}{}
\end{table}

@@

The force-distance curves show a general trend of repulsive forces
at small distances (Figure \ref{fig:Single-bridge}a). This is a result
of the pinned contact line on the top. A limited volume is available
for the liquid to occupy when the gap distance is small, causing the
meniscus shape to bulge outwards near the pinned contact line. This
creates a net positive curvature, resulting in a positive Laplace
pressure and thus repulsion. Without pinning, the capillary forces
would have shown high attractive forces on a hydrophilic substrate\citep{RN93}. 
It is reasonable to expect the contact line to be mechanically pinned around the rim of the discoidal-shaped hair tip.
Since the male ladybug's pads are majorly composed of discoidal hairs, we proceed with this assumption to estimate the net adhesion
force of the whole pad.
%CHECK EVERYWHERE SHOULD BE DIMENSIONAL!
\subsection{Adhesion of a hairy pad: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}

@@

We observed that the bubble itself does not contribute much to the net force
on either substrate (Figure \ref{fig:Effect-of-substrate}). Its contribution
even is slightly repulsive on the hydrophilic substrate due to the
positive curvature of the bubble, and slightly attractive on the hydrophobic
substrate due to its negative curvature. This small contribution is
manifested by the slightly higher adhesion for \emph{underwater: bubble}
relative to \emph{in air} for the hydrophobic substrate, since all
hairs are within the bubble in this case.
